Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-05 main.Rmd
all figure caption clean

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="Illustration of time domain, linear granularities and index set.  Hour, day, week, month and year are linear granularities and can also be considered to be time domains. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating. Hours could also be considered the index set, and a bottom granularity. "}
```

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap="Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences."}

@@

@@

```{r aperiodic-example, echo=FALSE, out.width = "100%", fig.cap = "Quasi-circular and aperiodic cyclic granularities illustrated through linear (a) and stack (b) display of time. The linear display shows linear granularities days, weeks, semester weeks, semester week type distributed linearly from past to future. Here a semester lasts for 18.3 weeks, each starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 1.3 weeks. This pattern remains same for all semester and hence $Q_{H, M}$ with $P$ = 18.3 weeks will be a quasi-circular granularity with repeating patterns. $A_{B, M}$ will be an aperiodic cyclic granularity since the placement of the semester within an year varies across years."}

@@

```{r data-structure, fig.cap = "The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.", fig.pos="htb"}
```

@@

```{r allFig, out.width="100%", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap="Distribution of energy consumption displayed through letter value plots. Plot (a) displays consumption across month-of-year faceted by quarters of the year, (b) across weekday/weekend faceted by quarters of the year and (c) across quarters of the year faceted by weekday/weekend. Plots (b) and (c) both show harmonies since each quarter consists of both weekdays and weekends. Conversely, weekend and weekday can occur in every quarter. Analysts should avoid plotting such clashes. Plot (b) helps to compare weekends and weekdays for each quarter. It can be seen that for every quarter weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently, whereas, Plot (c) helps to compare quarters within weekdays and weekends. For example, the quartile spread of consumption shrinks/lowers from first to fourth quarter for weekdays, whereas this pattern is not true for weekends. Plot (a) shows a clash since all quarters do not correspond to all months of the year. ", fig.show = 'hold'}

@@

@@

```{r bothcust, fig.cap = "Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: hour of the day (I) and weekday/weekend (II). Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping. Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots. Generally, on a work day there is more consumption early in the day.  Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays. Plot (c) uses a violin plot to place emphasis on distributional differences across hours. It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.", out.width="90%"}
```

@@

```{r cricex, fig.cap= "Runs per over shown with different distribution displays, and granularities. Plot (a) shows letter value plot across overs faceted by innings. For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over. This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.", warning = FALSE, message = FALSE, out.width = "90%"}

@@

>>>>

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="(ref:linear-time)"}
```

(ref:linear-time) Illustration of time domain, linear granularities and index set.  Hour, day, week, month and year are linear granularities and can also be considered to be time domains. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating. Hours could also be considered the index set, and a bottom granularity.

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap= "(ref:circular-dow)"}

@@

(ref:circular-dow) Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences.

@@

```{r aperiodic-example, echo=FALSE, out.width = "100%", fig.cap= "(ref:aperiodic-example)"}

```
(ref:aperiodic-example)  Quasi-circular and aperiodic cyclic granularities illustrated through linear (a) and stack (b) display of time. The linear display shows linear granularities days, weeks, semester weeks, semester week type distributed linearly from past to future. Here a semester lasts for 18.3 weeks, each starting with one week of orientation followed by an in-session period of 6 weeks, a semester-break of 1 week and again an in-session period of 7 weeks and 1 week study break before final exams which continue for 1.3 weeks. This pattern remains same for all semester and hence $Q_{H, M}$ with $P$ = 18.3 weeks will be a quasi-circular granularity with repeating patterns. $A_{B, M}$ will be an aperiodic cyclic granularity since the placement of the semester within an year varies across years.

@@

```{r data-structure, fig.cap = "(ref:data-structure)", fig.pos="htb"}
```

(ref:data-structure) The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.

@@

```{r allFig, out.width="100%", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap= "(ref:allFig)", fig.show = 'hold'}

@@

(ref:allFig) Distribution of energy consumption displayed through letter value plots. Plot (a) displays consumption across month-of-year faceted by quarters of the year, (b) across weekday/weekend faceted by quarters of the year and (c) across quarters of the year faceted by weekday/weekend. Plots (b) and (c) both show harmonies since each quarter consists of both weekdays and weekends. Conversely, weekend and weekday can occur in every quarter. Analysts should avoid plotting such clashes. Plot (b) helps to compare weekends and weekdays for each quarter. It can be seen that for every quarter weekend and weekday consumption are fairly similar except for the second quarter where the letter values below D and E behave differently, whereas, Plot (c) helps to compare quarters within weekdays and weekends. For example, the quartile spread of consumption shrinks/lowers from first to fourth quarter for weekdays, whereas this pattern is not true for weekends. Plot (a) shows a clash since all quarters do not correspond to all months of the year.

@@

```{r bothcust, fig.cap = "(ref:bothcust)", out.width="90%"}
```

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: hour of the day (I) and weekday/weekend (II). Plot (a) shows granularity I facetted by granularity II, and plots (b), (c) shows the converse mapping. Plot (a) makes a comparison of usage by workday within each hour of the day using side-by-side boxplots. Generally, on a work day there is more consumption early in the day.  Plots (b) and (c) examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot (b) uses an area quantile to put the emphasis on the time series, for example, the median consumption over time shows prolonged usage in the morning on weekdays. Plot (c) uses a violin plot to place emphasis on distributional differences across hours. It can be seen that the morning use on weekdays is bimodal, some work days there is low usage, which might indicate the person is working from home and also having a late start.

@@

```{r cricex, fig.cap= "(ref:cricex)", warning = FALSE, message = FALSE, out.width = "90%"}

@@

(ref:cricex) Runs per over shown with different distribution displays, and granularities. Plot (a) shows letter value plot across overs faceted by innings. For the team batting in the first innings there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. Plot (b) shows quantile plot of runs per over across an indicator of wickets in previous over faceted by current over. This indicates that at least one wicket in the previous over leads to lower median run rate and quartile spread in the subsequent over.
